\documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{enumerate}
\usepackage{listings}
\usepackage{framed}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 2011 13:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
\lhead{Maths Resource} \rhead{Probability Distributions}
\chead{Tutorial Sheet B}
%\input{tcilatex}

\begin{document}

\begin{enumerate}

\item 
A machine is used to package bags of potato chips.  Records of the packaging machine indicate that its fill weights are normally distributed with a mean of 455 grams per bag and a standard deviation of 10 grams.

    \begin{enumerate}[(i)]
    \item  What proportion of bags filled by this machine will contain more than 470 grams in the long run?
    \item What proportion of bags filled by this machine will contain less than 445 grams in the long run?
    \item What proportion of bags filled by this machine will be between 465 grams and 475 grams in the long run?
    \end{enumerate}
    
    
\item 
Telephone calls arrive at a switchboard at a rate of 30 per hour.  Assume that the switchboard operators take 2 minutes to deal with a customer query. Calculate the following:

\begin{enumerate}[(a)]
\item The probability of 2 or more calls arriving in any 4 minute period,
\item  The probability of no phone calls arriving in a 4 minute period,
\item  The probability of exactly three phone call arriving in a 10 minute period.
%\item [iv.]	The average and standard deviation of the number of phone calls arriving in a 2 minute period.    
\end{enumerate}



\item Under what circumstances is it appropriate to use the binomial distribution when calculating probabilities?				

\item 	Flextronics supply PCB boards to Dell.  You are a production manager with Dell.  There is a constant probability of 0.01 that a board will be defective.  You select 20 boards at random.  What is the probability that:

\begin{enumerate}[(a)]
\item 	0 boards will be defective
\item	1 or more boards will be defective
\item	2 or less boards will be defective			
\end{enumerate}

\item Flaws occur in an LCD display at the rate of 0.5 per square mm.  Calculate the probability that:
\begin{enumerate}[(a)]
\item exactly 2 flaws will occur in a square mm section
\item exactly 3 flaws will occur in a 5 square mm section
\item 5 or more flaws will occur in a 10 square mm section
\end{enumerate}
\item There is a constant probability of 0.05 that the power supply in a server network will fail.  You are required to calculate the probability that the power supply will fail the 4th time it is switched on.

\end{enumerate}
\end{document}
