 \documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{multicol}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{framed}
\usepackage{subfigure}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 2011 13:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

%\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
%\lhead{MA4413 2013} \rhead{Mr. Kevin O'Brien}
%\chead{Midterm Assessment 1 }
%\input{tcilatex}

\begin{document}

% Spring 2007
%=========================================%

\begin{enumerate}
\item 
	
	A company obtains 2000 components/week from supplier A, 2000 components/week from supplier B and 1000 components/week from supplier C. 3\% of the components from supplier A are defective, 4\% of the components from supplier B and 5\% of the components from supplier C.
	
	\begin{itemize}
		\item Calculate the probability that a randomly chosen component is defective.
		
		\item  Calculate the probability that the component is from supplier A, given that it is not defective.
		(6 marks)
	\end{itemize}
	
\item A company obtains 1500 components/week from supplier A, 1000 components/week from supplier B and 500 components/week from supplier C. 3\% of the components from supplier A are defective, 5\% of the components from supplier B and 6\% of the components from supplier C.

\begin{itemize}
\item[(a)]  Calculate the probability that a randomly chosen component is defective.

\item[(b)] description Calculate the probability that the component is from supplier C, given that it is defective.
\end{itemize}
%--------------------------%
\item On completion of a programming project, four programmers from a
team submit a collection of subroutines to an acceptance group. The
following table shows the percentage of subroutines each programmer
submitted and the probability that a subroutine submitted by each
programmer will pass the certification test based on historical data.
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
% after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
Programmer & 1 & 2 & 3 & 4 \\
Proportion of subroutines submitted & 0.10 & 0.20 & 0.40 & 0.30 \\
Probability of acceptance & .55 & .60 & .95 & .75 \\
\hline
\end{tabular}
\end{center}
\begin{itemize}
\item[a.] What is the proportion of subroutines that pass the acceptance test?
\item[b.] After the acceptance tests are completed, one of the subroutines is
selected at random and found to have passed the test. What is the
probability that it was written by Programmer l?
\end{itemize}


\item 

A computer manufacturer produces hard drives for laptops at plants located in Cork, Glasgow and Budapest; 40\% in Cork, 35\% in Glasgow and the remaining 25\% in Budapest. The probability that a hard drive will be found to be defective upon receipt by a customer is 0.005 if shipped from Cork, 0.01 if shipped from Glasgow, and 0.02 if shipped from Budapest.

\begin{itemize}
	\item (i)	What is the probability that a hard drive selected at random at a customer location will be found to be defective?
	\item (ii)	Suppose a hard drive selected at random is found to be defective upon arrival at a customer location. What is the probability that it was manufactured in Cork?
\end{itemize}
\item
	On completion of a programming project, three programmers from a team submit a collection of subroutines to an acceptance group. \\
	\\
	The following table shows the percentage of subroutines each programmer submitted and the probability that a subroutine submitted by each programmer will pass the certification test based on historical data.
	
	\begin{center}
		\begin{tabular}{|l|c|c|c|}
			\hline
			Programmer &	A	&B	& C	\\\hline
			Proportion of subroutines submitted&	0.40	&0.35	&0.25	\\ \hline
			Probability of acceptance	&0.75	&0.95	&0.85\\
			
			\hline
		\end{tabular}
	\end{center}

\begin{itemize}
	\item[i.] (3 marks) What is the proportion of subroutines that pass the acceptance test?
	\item[ii.](3 marks)  After the acceptance tests are completed, one of the subroutines is selected at random and found to have passed the test. What is the probability that it was written by Programmer A?
\end{itemize}




\end{enumerate}

\end{document}
