%========================================================%
	\subsection*{Question 7 - Sampling without Replacement (Solution Provided)}
	A lot of 100 semiconductor chips contains 20 that are defective.
	Two chips are selected at random, without replacement from the lot.
	\begin{enumerate}[(i)]
		\item What is the probability that the first one is defective? \\(Answer : 20/100 , i.e 0.20)
		\item What is the probability that the second one is defective given that the first one was defective? \\(Answer: 19/99)
		\item What is the probability that the second one is defective given that the first one was not defective? \\(Answer: 20/99)
	\end{enumerate}
	
	

%----------------------------------------------------------------%
\subsection{Probability Question}
In a class of 20 pupils, 11 have dark hair, 7 have fair hair and 2 have red hair.

Two pupils are chosen at random to collect the homework. What is the probability that they

\begin{itemize}
	\item[(a)] both have fair hair
	
	(3 marks)
	
	\item [(b)] each have hair of a different colour
	
	(4 marks)
\end{itemize}


(Marks available: 7)

Answer outline and marking scheme for question: 2

a) 21/190

(3 marks)

b) 226/380

(4 marks)

\newpage

\subsection*{Question 2}
Assume that 40\% of emails you receive can be classed as ``spam''. Your spam filter places 90\% of spam emails in the spam folder and 1\% of non-spam emails in the spam folder.\\[-0.2cm]


\item Using appropriate notation, convert the above into mathematical statements. \quad \item What proportion of your emails go to the spam folder? \quad \item Given that an email is in the spam folder, what is the probability that it is in fact spam? \quad \item Given that the email is \emph{not} in the spam folder, what is the probability that it is spam?


\subsection*{Question 3}
Let's assume you have four shirts (green, red, brown, black), two jackets (blue, black) and two pairs of trousers (brown, black).\\[-0.2cm]

\item How many outfits have you got altogether? \quad \item What if the shirt must be red? \quad \item What if the shirt must be green or black? \quad \item What if the shirt must be green and the jacket must be blue? \quad \item What if no item is to be black? \quad \item What if at least one item must be black? \quad \item What if the shirt and jacket can be the same colour but the trousers must be a different colour?


\subsection*{Question 4}
You must create a password of length 5 using the following characters:
$\{a,b,c,d,1,2,3,4\}$.\\[-0.2cm]

\item How many possible passwords are there? \quad \item What if you only use letters? \quad \item What if first character cannot be a number? \quad \item How many passwords contain \emph{at least one} number? \quad \item What if each character must be different?


\subsection*{Question 5}
In your favourite RPG game, let's assume that in selecting your character there are 5 character classes and 2 genders. Let's also assume there are 3 levels of difficulty for this game.\\[-0.2cm]

\item How many possible ways can you play this game? \quad \item What if you always choose the ``warrior'' class? \quad \item What if you always choose a female character? \quad \item What if you always play on the highest difficulty setting? \quad \item Let's assume the game has a two-player mode. How many possible ways can you play this game? (hint: you cannot play the game on different difficulty levels). \item What if your friend chooses a different character class to you?


\subsection*{Question 6}
Assume that you are going to an exam and you can only bring 3 items. You have the following items: $\{\text{mobile phone, } \text{pen, } \text{ruler, } \text{calculator, } \text{laptop, } \text{apple} \}$.

\item In order to make your decision, you first \emph{arrange} these 6 items on your desk. How many possible arrangements are there? \quad \item How many possible groups of three items can you bring with you? \quad \item What if you decide that the pen is essential? \quad \item What if the pen is essential and you also decide that you won't bring an apple or a laptop?


\subsection*{Question 7}
A team of 5 people is required to perform a particular task. We are selecting from a group of 7 women and 3 men.\\[0.2cm]
How many selections are there:

\item Altogether? \quad \item If one of the men is an expert and must be on the team? \quad \item If two of the individuals do not get along and cannot be on the team together? \quad \item If the group must contain 3 women and 2 men? \item If the group must contain more women than men? \quad \item If the group must contain more men than women?




