\documentclass[12pt, a4paper]{article}
\usepackage{natbib}
\usepackage{vmargin}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{subfigure}
%\usepackage{amscd}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{amsthm, amsmath}
%\usepackage[dvips]{graphicx}

\renewcommand{\baselinestretch}{1.8}

% left top textwidth textheight headheight % headsep footheight footskip
\setmargins{3.0cm}{2.5cm}{15.5 cm}{23.5cm}{0.5cm}{0cm}{1cm}{1cm}

\pagenumbering{arabic}


\begin{document}
\author{Kevin O'Brien}

MA4005 Syllabus
\begin{itemize}
\item Functions of several variables and partial differentiation.
\item The indefinite integral. Integration techniques: of standard functions, by substitution, by parts and using partial fractions.
\item The definite integral. Finding areas, lengths, surface areas, volumes, and moments of inertial.
\item Numerical integration: trapezoidal rule, Simpson's rule.
\item Ordinary differential equations.
\item First order including linear and separable. Linear second order equations with constant coefficients.
\item Numerical solution by Runge-Kutta. 
\item The Laplace transform: tables and theorems and solution of linear ODEs.
\item Fourier series: functions of arbitary period, even and odd functions, half-range expansions.
\item Application of Fourier series to solving ODEs.
\item Matrix representation of and solution of systems of linear equations.
\item Matrix algebra: invertibility, determinants.
\item Vector spaces: linear independence, spanning, bases, row and column spaces, rank.
\item Inner products: norms, orthogonality. Eigenvalues and eignenvectors.
\item Numerical solution of systems of linear equations. Gauss elimination, LU decomposition, Cholesky decomposition,
iterative methods. Extension to non-linear systems using Newton's method.
\end{itemize}
\newpage
\subsection*{Trigonometric Subsititution}
\[\int\frac{dx}{\sqrt{a^2-x^2}}\]

\[x=a\sin(\theta),\quad dx=a\cos(\theta)\,d\theta, \quad \theta=\arcsin\left(\frac{x}{a}\right)\]

{\large
\begin{eqnarray}
\int\frac{dx}{\sqrt{a^2-x^2}} & = \int\frac{a\cos(\theta)\,d\theta}{\sqrt{a^2-a^2\sin^2(\theta)}}\\ \nonumber &= \int\frac{a\cos(\theta)\,d\theta}{\sqrt{a^2(1-\sin^2(\theta))}} \\ \nonumber
& = \int\frac{a\cos(\theta)\,d\theta}{\sqrt{a^2\cos^2(\theta)}} \\ &= \int d\theta=\theta+C \\ \nonumber &=\arcsin\left(\frac{x}{a}\right)+C
\end{eqnarray}
}

\subsection*{Augmented Matrices}
Given the matrices $A$ and $B$, where

\[
A =
  \begin{bmatrix}
    1 & 3 & 2 \\
    2 & 0 & 1 \\
    5 & 2 & 2
  \end{bmatrix}
, \quad
B =
  \begin{bmatrix}
    4 \\
    3 \\
    1
  \end{bmatrix},
\]

the augmented matrix ($A|B$) is written as

\[
(A|B)=
  \left[\begin{array}{ccc|c}
    1 & 3 & 2 & 4 \\
    2 & 0 & 1 & 3 \\
    5 & 2 & 2 & 1
  \end{array}\right].
\]

This is useful when solving systems of linear equations.


\begin{eqnarray} \nonumber
x + 2y + 3z = 0 \\ \nonumber
3x + 4y + 7z = 2 \\ \nonumber
6x + 5y + 9z = 11 \nonumber
\end{eqnarray}

the coefficients and constant terms give the matrices
\[
A =
\begin{bmatrix}
1 & 2 & 3 \\
3 & 4 & 7 \\
6 & 5 & 9
\end{bmatrix}
, \quad
B =
\begin{bmatrix}
0 \\
2 \\
11
\end{bmatrix},
\]

and hence give the augmented matrix
\[
(A|B) =
  \left[\begin{array}{ccc|c}
1 & 2 & 3 & 0 \\
3 & 4 & 7 & 2 \\
6 & 5 & 9 & 11
  \end{array}\right]
\]

\[\left[\begin{array}{ccc|c}
1 & 0 & 0 & 4 \\
0 & 1 & 0 & 1 \\
0 & 0 & 1 & -2 \\
  \end{array}\right]\]
  
\subsection*{Reduced Row Echelon Form}

Specifically, a matrix is in row echelon form if
\begin{itemize}
\item All nonzero rows (rows with at least one nonzero element) are above any rows of all zeroes (all zero rows, if any, belong at the bottom of the matrix).
\item The leading coefficient (the first nonzero number from the left, also called the pivot) of a nonzero row is always strictly to the right of the leading coefficient of the row above it.
\item All entries in a column below a leading entry are zeroes (implied by the first two criteria).[1]
\end{itemize}
\[\left[ \begin{array}{ccccc}
1 & a_0 & a_1 & a_2 & a_3 \\
0 & 0 & 1 & a_4 & a_5 \\
0 & 0 & 0 & 1 & a_6
\end{array} \right]\]
\newpage
%-------------------------------%
\subsection*{Newton-Raphson Method}
\[x_{1} = x_0 - \frac{f(x_0)}{f'(x_0)}\]
\[x_{n+1} = x_n - \frac{f(x_n)}{f'(x_n)} \]

\section*{Numerical Integration}
Numerical integration constitutes a broad family of algorithms for calculating the numerical value of a definite integral, and by extension, the term is also sometimes used to describe the numerical solution of differential equations.
\subsection*{Numerical Integration: Simpson's Rule}
\[\int_{a}^{b} f(x) \, dx \approx \frac{b-a}{6}\left[f(a) + 4f\left(\frac{a+b}{2}\right)+f(b)\right].\]


\subsection*{Trapezoidal Rule}
\[\int_{a}^{b} f(x)\, dx \approx (b-a)\frac{f(a) + f(b)}{2}\]

%-------------------------------%
\subsection*{Laplacian Analysis: convolution}

\[ (f * g)(t) = \int_0^t f(\tau)g(t-\tau)\,d\tau= F(s) \cdot G(s) \]

%-------------------------------%
\subsection{ODEs: Integrating factor}
The integrating factor is a function that is chosen to facilitate the solving of a given equation involving differentials. It is commonly used to solve ordinary differential equations.

\[ y'+ P(x)y = Q(x)\]

the integration factor is 
\[M(x) = e^{\int P(x') dx'}\]


\subsection*{ODEs: Example}

Solve the differential equation

\[y'-\frac{2y}{x} = 0.\]

We can see that in this case \[P(x) = \frac{-2}{x}\]

\[ M(x)=e^{\int P(x)\,dx}\]

\[ M(x)=e^{\int \frac{-2}{x}\,dx} = e^{-2 \ln x} = {(e^{\ln x})}^{-2} = x^{-2} \] (Note we do not need to include the integrating constant - we need only a solution, not the general solution)

\[ M(x)=\frac{1}{x^2}.\]

Multiplying both sides by \[M(x)\] we obtain

\[\frac{y'}{x^2} - \frac{2y}{x^3} = 0\]

\[\frac{y'x^3 - 2x^2y}{x^5} = 0\]

\[\frac{x(y'x^2 - 2xy)}{x^5} = 0\]

\[\frac{y'x^2 - 2xy}{x^4} = 0.\]


%-------------------------------%
\subsection{Partial Derivatives: Volume of a Cone}

The volume ''V'' of a cone depends on the cone's height ''h'' and its radius 'r' according to the formula
\[V(r, h) = \frac{\pi r^2 h}{3}.\]
The partial derivative of ''V'' with respect to 'r' is
\[\frac{ \partial V}{\partial r} = \frac{ 2 \pi r h}{3},\]

which represents the rate with which a cone's volume changes if its radius is varied and its height is kept constant.
The partial derivative with respect to ''h'' is
\[\frac{ \partial V}{\partial h} = \frac{\pi r^2}{3},\]

which represents the rate with which the volume changes if its height is varied and its radius is kept constant.
\section{Fundamental Theorem of Calculus}
The fundamental theorem of calculus states that the integral of a function f over the interval $[a, b]$ can be calculated by finding an antiderivative F of f:
\[\int_a^b f(x)\,\mathrm dx = F(b) - F(a).\]

\section{Curl}
In vector calculus, the curl is a vector operator that describes the infinitesimal rotation of a 3-dimensional vector field. At every point in the field, the curl of that field is represented by a vector. The attributes of this vector (length and direction) characterize the rotation at that point.
%--------------------------------------------------%
\section{Laplacian Operator}
\[\Delta f = \nabla^2 f = \nabla \cdot \nabla f\]

%--------------------------------------------------%
\section{Notation}
\[ \begin{vmatrix} \mathbf{i} & \mathbf{j} & \mathbf{k} \\
{\frac{\partial}{\partial x}} & {\frac{\partial}{\partial y}} & {\frac{\partial}{\partial z}} \\
 F_x & F_y & F_z \end{vmatrix}\]

\[\left(\frac{\partial F_z}{\partial y}  - \frac{\partial F_y}{\partial z}\right) \mathbf{i} + \left(\frac{\partial F_x}{\partial z} - \frac{\partial F_z}{\partial x}\right) \mathbf{j} + \left(\frac{\partial F_y}{\partial x} - \frac{\partial F_x}{\partial y}\right) \mathbf{k}\]

 %--------------------------------------------------%
\section{Example}
\[f(x,y,z)= \ 2x+3y^2-\sin(z)\]

\[ \nabla f=
\frac{\partial f}{\partial x} \mathbf{i} +
\frac{\partial f}{\partial y} \mathbf{j} +
\frac{\partial f}{\partial z} \mathbf{k}
 = 2\mathbf{i}+ 6y\mathbf{j} -\cos(z)\mathbf{k}\]

\section{Stoke's Theorem}
\[
\iint_{\Sigma} \nabla \times \mathbf{F} \cdot d\mathbf{\Sigma} = \oint_{\partial\Sigma} \mathbf{F} \cdot d \mathbf{r}, \]

\section{Laplace Transforms }
If $g(t)=k \times f(t)$ then $G(S) = k \times F(S)$ where $k$ is a
constant. $\mathcal{f(t)}=F(S)$.
\begin{eqnarray}
f(t) &=& (t+1)^2\\
&=& t^2 +2t +1 \nonumber
\end{eqnarray}


\section{Laplace Transforms Using 1st Shifting Theorem}
\begin{eqnarray}
 g(t) = e^{at}f(t) \quad \Leftrightarrow \quad G(S)= F(S-a) \nonumber
\end{eqnarray}
The function $g(t)$ is presented in a form whereby $a$ and $f(t)$
are easily identifiable. First determine $F(S)$ by finding the
Laplace transform of $f(t)$. Then replace all $S$ terms with
$S-a$.

\section{Laplace Transforms Using 2nd Shifting Theorem}

\begin{eqnarray}
 g(t) = u^{a}f(t-a) \quad \Leftrightarrow \quad G(S)= e^{-aS}F(S) \nonumber
\end{eqnarray}
The function $g(t)$ is presented in a form whereby $a$ and
$f(t-a)$ are easily identifiable. ($U_{a}(t)$ is called the unit
step function). First determine $f(t)$ by replace all $t-a$ terms
in $f(t-a)$ with $t$. Then calculate the laplace transform of
$f(t)$ i.e. $F(S)$. The solutions is in form $G(S)= e^{-aS}F(S)$.

\section{Inverse Laplace Transforms (2 questions) }
Partial fraction expansion is used in questions 4 and 5.
\section{Inverse Laplace Transforms 2}

The denominator has form $S^2 - 2aS + a^2 + k$ which is equivalent
to $(S-a)^2 + k$. Therefore $G(S)$ will have form $F(S-a)$
\newline
The function $G(S)$ may have the form $\frac{S+D}{S^2 +(C+D)S +
CD}$, where C and D are constants. This expression simplifies
$\frac{S+D}{(S+C)(S+D)}$ and again to $\frac{1}{S+C}$. The inverse
laplace transform $g(t)$ can be easily determined.
\section{Convolution}
We are asked to find a function h(t) which is the convolution of
two given functions $f(t)$ and $g(t)$. i.e $h(t)=h*g(t)$.\newline
Importantly $H(S) = F(S)\times G(S)$. We determine the laplace
transforms, F(S) and G(S), and multiply them to determine H(S). We
then find the inverse Laplace transform of H(S) to yield our
solution.
\subsection{Example}
Find $h(t)$ when $h(t) = f*g(t)$, with $f(t)= e^{t}$ and $g(t)=
e^{-t}$.\newline

\begin{eqnarray}
f(t) = e^{t} \quad \Leftrightarrow \quad F(S)= \frac{1}{S-1}
 \nonumber\\
g(t) = e^{-t} \quad \Leftrightarrow \quad G(S)= \frac{1}{S+1}
 \nonumber\\
H(S) = F(S)\times G(S) = \frac{1}{(S-1)(S+1)}
 \nonumber
\end{eqnarray}
\subsection{Example}
Find $h(t)$ when $h(t) = f*g(t)$, with $f(t)= t$ and $g(t)=
t^2$.\newline

\begin{eqnarray}
f(t) = t \quad \Leftrightarrow \quad F(S)= \frac{1}{S^2}
 \nonumber\\
g(t) = t^2 \quad \Leftrightarrow \quad G(S)= \frac{2}{S^3}
 \nonumber\\
H(S) = F(S)\times G(S) = \frac{2}{S^5}
 \nonumber\\
(H(S) \mbox{ is in form }  k\frac{n!}{S^{n+1}} )
 \nonumber
\end{eqnarray}

With $n=4$, $n!= 4! = 24$. Solving for $k$, $k \times n! = 2$.
Therefore $k=\frac{1}{12}$. The solution is $\cal{L}^{-1}[H(S)]$

\section{Period of a trigonomteric function}
Period of a function is denoted $2l$. (Sometimes it is denoted as
$L$, with $L=2l$). \newline When given a trigonometric function in
form $f(t) = Cos(kx)$ or $f(t)= Sin(kx)$, the period of the
function can be calculated as follows:

\begin{eqnarray}
2l = \frac{2 \pi}{k}\nonumber
\end{eqnarray}


\subsection{Example}
\begin{eqnarray}f(t) = Cos(\frac{2 \pi x}{3}) \nonumber\\
2l \quad=\frac{2\pi}{(\frac{2\pi}{3})}\quad =
\frac{1}{(\frac{1}{3})}\quad= \textbf{3}\nonumber
\end{eqnarray}

\subsection{Example}
\begin{eqnarray}f(t) = Sin(\frac{5x}{2}) \nonumber\\
2l \quad=\frac{2\pi}{(\frac{5}{2})}\quad = \frac{4\pi}{5}\nonumber
\end{eqnarray}

\section{Even and Odd Function}
Even Functions: $Cos(X)$ ,$|X|$ (i.e absolute value of $X$) and
$X^2$, $X^4$ etc
\newline
Odd Functions: $Sin(X)$, $X$, $X^3$ etc
\\
Functions that are products of two even functions are also
\textbf{even} functions.
\newline
Functions that are products of two odd functions are
\textbf{even} functions. (e.g $X \times X^3 = X^4$)
\newline
Functions that are products of an even function and an
odd function are \textbf{odd} functions.
\section{Fourier Series - determining the arguments}
Given a period $2l$, we must determine the form of the fourier
series. $sin( \frac{n x \pi}{l})$
\section{Fourier Series}
X


\end{document}
