%===============================================================%
\newpage
\subsection*{Question 4}


Q4. (a) Discuss the statement “Correlation does not imply causation” within the context of data analysis. (4 marks)



%===============================================================%
\newpage
(b) An insurance company is interested in estimating the relationship between the rebuild cost of a detached house and the size of the house measured in square metres. Rebuild quotations were provided for a sample of 14 detached houses. The following data with summary measures were obtained:

House size (x) 70 83 74 93 140 85 114 95 100 111 140 161

Rebuild cost (y) 80 90 100 110 320 150 160 180 200 250 270 320

\begin{itemize}

\item[(i)] Describe the relationship between house size and rebuild cost using the scatter plot below. % (1 mark)

\item[(ii)] Compute the Pearson correlation coefficient. Interpret this value.  %(2 marks)

\item[(iii)] Determine the least squares regression equation. Interpret the meaning of the slope of the regression line. (4 marks)

\item[(iv)] Use the regression line to estimate the rebuild cost for a house sized 120 square metres. %(2 marks)

\item[(v)] Using the 5% significance level, test the significance of the slope. Interpret the result.  %(6 marks)

\item[(vi)] Calculate and interpret the coefficient of determination.  %(3 marks)

\item[(vi)] What assumptions should a regression model satisfy? How can these assumptions be checked?  %(3 marks)

\end{itemize}

\end{document}
%============================================================================%
