\documentclass[]{report}

\voffset=-1.5cm
\oddsidemargin=0.0cm
\textwidth = 480pt

\usepackage{framed}
\usepackage{subfiles}
\usepackage{graphics}
\usepackage{newlfont}
\usepackage{eurosym}
\usepackage{amsmath,amsthm,amsfonts}
\usepackage{amsmath}
\usepackage{color}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\begin{document}
\section*{Discrete Random Variables}
	\begin{enumerate}
		\item  On a roulette wheel there are 37 numbers {0,1,…,36}. 18 numbers are black. If I bet €1 on black, I win €1 if a black number comes up, otherwise I lose my stake. Let X denote my winnings on one bet.
		\begin{itemize}
		\item[(i)]	Calculate E(X) and Var(X)
		\end{itemize}
		
		
		Suppose I make 6 such bets. Let Y denote my total winnings. 
	\begin{itemize}
		\item[(ii)]	Derive the distribution of Y.
	\item[(iii)]	Calculate E(Y) and Var(Y)
	\end{itemize}	

\item The probability distribute of discrete random variable $X$ is tabulated below. There are 5 possible outcome of $X$, i.e. 1, 2, 3, 4 and 5.
	\begin{center}
		\begin{tabular}{|c||c|c|c|c|c|}
			\hline
			$x_i$  & 1 & 2 & 3 & 4 & 5  \\\hline
			$p(x_i)$ & 0.30 & 0.20 & k & 0.10 & 0.20 \\
			\hline
		\end{tabular}
	\end{center}
	
	\begin{itemize}
		\item[a.] (1 Mark) Compute the value of $k$.
		\item[b.] (1 Mark) What is the expected value of X?
		%\item[c.] (1 Mark) Compute the value of $E(X^2)$
		\item[c.] (1 Mark) Given that $E(X^2) = 9.5$, compute the variance of $X$.
	\end{itemize}

	\item  The probability distribution of discrete random variable $X$ is tabulated below. There are 6 possible outcome of $X$, i.e. 0, 1, 2, 4 ,8 and 10.
	\begin{center}
		\begin{tabular}{|c||c|c|c|c|c|c|}
			\hline
			$x_i$  & 0 & 1 & 2 & 4 & 8 & 10 \\\hline
			$P(x_i)$ & 0.25 & 0.15 & 0.25 & 0.15 & k & 0.10\\
			\hline
		\end{tabular}
	\end{center}
	
	\begin{itemize}
		\item[i.] (1 marks) Compute the value for $k$.
		\item[ii.] (3 marks) Determine the expected value $E(X)$.
		\item[iii.] (2 marks) Evaluate $E(X^2)$.
		\item[iv.] (3 marks) Compute the variance of random variable $X$.
	\end{itemize}
	%---------------------------------------------------------- %
	%Question 2
	\item 
	Suppose $X$ is a random variable with 
	\begin{itemize}
		\item $E(X^2)=3.6$
		\item $P(X=2)=0.6$
		\item $P(X=3)=0.1$
	\end{itemize}
	
	\begin{itemize}
		\item[(a)] The random variable takes just one other value besides 2 and 3. This value is greater than 0. What is this value?
		\item[(b)] What is the variance of $X$?
	\end{itemize}
	

	
	%Question 6
	\item Consider the random variables $X$ and $Y$. Both $X$ and $Y$ take the values 0,$\;$1 and 2. 
	The joint probabilities for each pair are given by the following table.
	\begin{center}
		\begin{tabular}{|c|c|c|c|}
			\hline  & $X=0$ & $X=1$ & $X=2$ \\ 
			\hline $Y=0$ & 0.1 & 0.15 & 0.1 \\ 
			\hline $Y=1$ & 0.1 & 0.1 & 0.1 \\ 
			\hline $Y=2$ & 0.2 & 0.05 & 0.1 \\ 
			\hline 
		\end{tabular} 
	\end{center}
	Compute the $E(U)$ expected value of $U$, where $U=X-Y$.

\item 
	Suppose $X$ is a random variable with 
	\begin{itemize}
		\item $E(X^2)=3.6$
		\item $P(X=2)=0.6$
		\item $P(X=3)=0.1$
	\end{itemize}
	
	
	\begin{itemize}
		\item[(i)] The random variable takes just one other value besides 2 and 3. This value is greater than 0. What is this value?\\
		\item[(ii)] What is the variance of $X$?
	\end{itemize}

	
\item Consider the random variables $X$ and $Y$. $X$ takes the values 0,1 and 2. $Y$ takes the values $0$ and $1$.
	The joint probabilities for each pair are given by the following table.
	\begin{center}
		\begin{tabular}{|c|c|c|c|}
			\hline  & $X=0$ & $X=1$ & $X=2$  \\ 
			\hline $Y=0$ & 0.1  & 0.4 & 0.1 \\ 
			\hline  $Y=1$ & 0.1 & 0.1 & 0.2 \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\begin{itemize}
		\item Compute the expected values of $X$ and $Y$.
		\item Compute the $E(X|Y=1)$
	\end{itemize}
\end{enumerate}	
	%-----------------------------------------------------------------------------------%
\end{document}	
	
