\documentclass[]{report}

\voffset=-1.5cm
\oddsidemargin=0.0cm
\textwidth = 480pt

\usepackage{framed}
\usepackage{subfiles}
\usepackage{graphics}
\usepackage{newlfont}
\usepackage{eurosym}
\usepackage{amsmath,amsthm,amsfonts}
\usepackage{amsmath}
\usepackage{color}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\begin{document}
\section*{MathsResource.github.io - The Exponential Distribution}	
\section*{Question 1}

Assume that the time between arrivals of customers at a particular bank is exponentially distributed with a mean of 4 minutes. 

\begin{itemize}
\item[(i)]
Find the probability that the time between arrivals is greater than 5 minutes.
\item[(ii)]
Find the probability that the time between arrivals will be less than 1 minute.
\end{itemize}

\section*{Question 2}

Faults occur in a fibre optic cable at the rate of 0.5 per 10KM of cable.  Calculate the probability that:

\begin{itemize}
\item[(i)] Exactly 2 flaws will occur in a given 10KM section
\item[(ii)] 4 or more flaws will occur in a given 10KM section
\item[(iii)] Eircom are providing 100KM fibre optic connection between Limerick and Cork.  What is the probability of 7 or more flaws in the 100KM section?	
\end{itemize}				

\section*{Question 3}
The average lifespan ppf a laptop is 5 year. You may assume that the lifespan of laptop computers follows an exponential distribution.
\begin{itemize}
	\item[(i)] What is the probability that the lifespan of the laptop will be at least 6 years.
	\item[(ii)] What is the probability that the lifespan of the laptop will not exceed 4 years.
	\item[(iii)] What is the probability that the lifespan of the laptop will be between 5 years and 6 years.
\end{itemize}

\end{document}
