\documentclass[]{report}

\voffset=-1.5cm
\oddsidemargin=0.0cm
\textwidth = 480pt

\usepackage{framed}
\usepackage{subfiles}
\usepackage{graphics}
\usepackage{newlfont}
\usepackage{enumerate}
\usepackage{eurosym}
\usepackage{amsmath,amsthm,amsfonts}
\usepackage{amsmath}
\usepackage{color}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\begin{document}

%======================================================== 
\subsection*{Question 1}
%  Repeat 2007
The percentage of carbon in a batch of steel produced using a particular method is normally distributed with mean 2 and variance 0.09. 

\begin{enumerate}[(a)]
	\item Calculate the probability that the percentage of carbon in a batch is less than 2.15
	
	\item The batch is high grade if the percentage of carbon is between 1.7 and 2.3. Calculate the probability that the batch is high grade. 
	
	\item Suppose that it is possible to control the variance. What is the maximum variance possible such that at least 95\% of the batches are high grade?
\end{enumerate}

%======================================================== 
\subsection*{Question 2}
%% Repeat 2005 (question 2)(b)	
The compressive strength of concrete for fresh-water exhibition tanks has mean 5000 psi and standard deviation 240 psi. Assuming that the compressive strength is normally distributed, calculate the probability that the compressive strength of a sample of concrete is less than 4900 psi.


%----------------------------------------------------------------%
\subsection*{Question 3}
IQ scores are assumed to have a normal distribution with mean 100 and standard deviation 15.

\begin{enumerate}[(a)]
	\item What IQ would you have if you were in the 80th percentile?
	\item Estimate the threshold for the top 10 percent?
	\item What is the probability of having an IQ above 142?
	\item What is the probability of having an IQ below 97?
\end{enumerate}

%----------------------------------------------------%

\subsection*{Question 4}
A machine produces components whose thicknesses are normally
distributed with a mean of 0.40 cm and a standard deviation of 0.02 cm.
Components are rejected if they have a thickness outside the range 0.38 cm
to 0.41 cm.
\begin{enumerate}[(a)]
	\item What is the probability that a component will have a thickness
	exceeding 0.41 cm? 
	\item What is the probability that a component will have a thickness between
	0.38 cm and 0.41 cm?
	\item What is the thickness below which 25\% of the components will be?
\end{enumerate}
%----------------------------------------------------%

\subsection*{Question 5}
A charity believes that when it puts out an appeal for charitable donations the
donations it receives will normally distributed with a mean £50 and standard
deviation £6, and it is assumed that donations will be independent of each
other.
\begin{enumerate}[(a)]
	\item Find the probability that the first donation it receives will be greater
	than £40.
	\item Find the probability that it will be between £55 and £60.
	\item Find the value x such that 5\% of donations are more than £x.
\end{itemize}

%----------------------------------------------------%

\subsection*{Question 6}

The diameter of a screw produced in a factory has a normal distribution with mean 8mm and standard deviation 0.05mm. A screw is defective if its diameter is less than 7.92mm or more than 8.08mm.

\begin{enumerate}[(a)]
	\item Calculate the probability that a screw is defective.
	
	\item Suppose it is possible to control the variance of the diameter without changing the mean diameter. What is the maximum variance possible such that only 1\% of screws are defective?
	
\end{itemize}
%===================================================%
\subsection*{Question 7}
Assume that the number of weekly study hours for students at a certain university is approximately normally distributed with a mean of 22 and a standard deviation of 6.

\begin{enumerate}[(a)]
	\item Find the probability that a randomly chosen student studies less than 12 hours.
	\item Estimate the percentage of students that study more than 37 hours.
\end{enumerate}

%----------------------------------------------------%

\subsection*{Question 8}
%Repeat 2006 Q3.    (a) 	
Suppose an oil exploration company purchases drill bits that have a life span that is approximately normally distributed, with a mean equal to 80 hours and a standard deviation equal to 10 hours.

\begin{enumerate}[(a)]
	\item What is the probability that a drill bit will fail before 60 hours of use?
	
	\item What is the probability that a drill bit will last between 70 hours and 90 hours?
	
	\item The life span of 95\% of drill bits is below what value?
	
\end{enumerate}
 %----------------------------------------------------%

\subsection*{Question 9}
%- Spring 2006 Q3.    (a)	

The breaking strength of a certain type of plastic block is normally distributed with a
mean of 1500kg and standard deviation of 50kg. 

\begin{enumerate}[(a)]
	\item What is the probability that a block with have a breaking strength greater than 1570kg?
	\item What is the probability that a block with have a breaking strength measuring between 1482kg and 1518kg?
	\item Determine the maximum load such that no more than 5`\% of the blocks break?
\end{enumerate}


%========================================================
\subsection*{Question 10}
% %	MA4004     Engineering Statistics    SPRING 2008


The amount of beer in a bottle has a normal distribution with mean 500ml and variance 25ml$^2$.
\begin{enumerate}[(a)]
	\item Calculate the probability that the amount of beer in the bottle is between 498ml and 504ml.
	\item What volume is exceeded by $20\%$ of the bottles? 
	\end{enumerate}

%======================================================== %

\subsection*{Question 11}
%%	\noindent \textbf{MA4413 Autumn 2008 paper}

A model of an on-line computer system gives a mean times to retrieve a record from a direct access storage system device of 200 milliseconds, with a standard deviation of 58 milliseconds. If it can assumed that the retrieval times are normally distributed:

\begin{itemize}
	\item[(i)] What proportion of retrieval times will be greater than 75 milliseconds?
	\item[(ii)] What proportion of retrieval times will be between 150 and 250 milliseconds?
	\item[(iii)] What is the retrieval time below which 10\% of retrieval times will be?
\end{itemize}


	
\subsection*{Question 12}
Assume that the number of weekly study hours for students at a certain university is approximately normally distributed with a mean of 22 and a standard deviation of 6.

\begin{itemize}
	\item[i.] Find the probability that a randomly chosen student studies less than 12 hours.
	\item[ii.] Estimate the percentage of students that study more than 37 hours.
\end{itemize}


\subsection*{Question 13}

A scientific publishing house produces assembly manuals for kit cars. The number
of manuals sold every year is known to be normally distributed with a mean of 500 and a
standard deviation of 50.

\begin{enumerate}[(a)]
	\item What is the probability that the number of manuals sold will exceed 600?
	\item What is the probability that the number of manuals sold will be less than 300?
	\item What is the probability that the number of manuals sold will be between 450 and 550?
	\item What is the minimum number of manuals that the company must print such
	that that 90\% of the demand is satisfied?
\end{enumerate}
%========================================%
\subsection*{Question 14}
% \emph{Taken from MA4104 Business Statistics Examination paper, Spring % 2008 Question 1 part A}\\


A tyre manufacturer claims that under normal driving conditions, the tread life of a certain tyre follows a normal distribution with mean 50,000 miles and standard deviation 5000 miles.

\begin{enumerate}[(a)]
	\item If your tyres wear out at 45,000 miles, would you consider this unusual? Support your answer with an appropriate probability calculation using the normal curve. % [ 10 marks ]
	
	\item If the manufacturer sells 100,000 of these tyres and warrants them to last at least 40,000 miles, about how many tyres will wear out before the warranty expires?% [ 10 marks ]
\end{enumerate}

%========================================%
\subsection*{Question 15}
Suppose $X$ is a normally distributed random variable with mean $\mu =500$ and $\sigma = 24$.

\begin{enumerate}[(a)]
	\item Compute the value of $P(X \geq 518)$
	\item Compute the value of $P(X \leq 482)$
	\item Compute the value of $P(482 \leq X \leq 518)$
\end{enumerate}

\end{document}
